\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-04-20 doc/sw-system.tex
Add to section on going beyond training, closes #144

At this point, the distribution of lens and source properties are quite
realistic. We then chose to make cuts of the simulated lens pool, in order to
reject sims that were likely to be diﬃcult to spot. While this ensured the
educational value of the sims when feedback was given, it meant that we should
only expect to detect real lens candidates that also pass these cuts. Any real
lens candidates we ﬁnd with properties outside the ranges of the sims, may in
some sense be considered bonuses, a product of the {\it imagination} of the
crowd in extrapolating their understanding of gravitational lenses into a regime
where they have not seen any before. In the \cfhtls project, the most important
selection cuts were to only keep sims with a)  second brightest image brighter
that $i = 23$ and b) total combined image magnitude brighter than 19--20
(\PaperTwo, Table~1). The combination of these two cuts results in a sample of
visible lensed image configurations.

>>>>

At this point, the distribution of lens and source properties are quite
realistic. We then chose to make cuts of the simulated lens pool, in order to
reject sims that were likely to be diﬃcult to spot. While this ensured the
educational value of the sims when feedback was given, it meant that we should
only expect to detect real lens candidates that also pass these cuts. Indeed, for traditional machine learning or computer vision implementations then this would be a constraint, but human classifiers are capable of going beyond their training; Geach et al., for example (REF????) report the discovery of a red lens by volunteers who had only been trained on blue examples. This ability to go beyond training is a key advantage of human classifiers, and 
any real
lens candidates we ﬁnd with properties outside the ranges of the sims, may in
this sense be considered bonuses, a product of the {\it imagination} of the
crowd in extrapolating their understanding of gravitational lenses into a regime
where they have not seen any before. In the \cfhtls project, the most important
selection cuts were to only keep sims with a)  second brightest image brighter
that $i = 23$ and b) total combined image magnitude brighter than 19--20
(\PaperTwo, Table~1). The combination of these two cuts results in a sample of
visible lensed image configurations.
